Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
Instead of modifying filter h, let's introduce a separate filter

As computation trick, it appears that using a parametrized hard-threshold
filter slightly improves performances. Introducing the parameter $c$ in
function $h$ yields an optimized filter
\begin{align}
h^*(x^t_i) = (x_i^t)^c \text{ } \mathbb{1}(x_i^t \ge \tau) \text{ with } \tau > 0,
\end{align}
where $c$ is set to $0.9$ after experiments.

>>>>

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since most timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened the difference in peak magnitude through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yield slightly AUROC with $c=0.9 \in (0, 1)$.
